---
title: "p8105_hw1_xj2249"  
author: "jx2249"  
date: "2019/9/12"
output: github_document
editor_options: 
  chunk_output_type: console
---

# Problem 1 
## Create a data frame
```{r, message = FALSE}
library(tidyverse)
p1_df <- tibble(
                rnorm_sample = rnorm(8), 
                sample_pos = rnorm_sample > 0,
                character_vec = c(rep(c("dog","cat"),4)), 
                factor_vec = factor(c("a","b","c","a","b","c","a","b"))
                )
               
sapply(p1_df, mean)

```
It works to take the mean of the random sample and the logical variable, but it doesn't when it comes to the character and the factor variable.

## Apply the "as.numeric function"
```{r, eval = FALSE}
# convert the logical vector to numeric, and multiply the random sample by the result
as.numeric(pull(p1_df, sample_pos ))
# convert the logical vector to a factor, and multiply the random sample by the result
as.numeric(pull(p1_df, character_vec ))
# convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
as.numeric(pull(p1_df, factor_vec ))
```
As the result shows, the logical variable is able to be converted into numbers(1 or 0).  
The character variable and the factor variables are not allowed since in my case, they are neither numeric nor logical value, which explains why means can't be taken above.

## We're converting variables ! 
```{r }
as.numeric(pull(p1_df, sample_pos )) * pull(p1_df, rnorm_sample )
as.factor(pull(p1_df, sample_pos )) * pull(p1_df, rnorm_sample )
as.numeric(as.factor(pull(p1_df, sample_pos ))) * pull(p1_df, rnorm_sample )
```

# Problem 2
## Create a new data frame
```{r}
p2_df <- tibble(
                x = rnorm(500), 
                y = rnorm(500),
                sum_compare = (x + y) > 1, 
                numeric_sum = as.numeric(sum_compare),
                factor_sum = as.factor(sum_compare)
                )
```

* The size of the dataset is `r nrow(p2_df)` and `r nrow(p2_df)`
* The mean, median, and standard deviation of x are
`r mean(pull(p2_df,x)) `, `r median(pull(p2_df,x)) ` and `r sd(pull(p2_df,x))`
* The proportion of cases for which x + y > 1 is `r mean(pull(p2_df,numeric_sum))`

## Make scatterplots of y vs x
```{r, message = FALSE}
library(ggplot2)
plot1 <- 
        p2_df %>% 
        ggplot(aes(x = x, y = y, color = sum_compare)) + 
        geom_point() + 
        labs(title = "The first scatterplot") + 
        theme(plot.title = element_text(hjust = 0.5))
        
plot1 
plot2 <- p2_df %>% 
         ggplot(aes(x = x, y = y, color = numeric_sum)) + 
         geom_point() + 
         labs(title = "The second scatterplot") + 
         theme(plot.title = element_text(hjust = 0.5))
plot2 
plot3 <- p2_df %>% 
         ggplot(aes(x = x, y = y, color = factor_sum)) + 
         geom_point() + 
         labs(title = "The third scatterplot") +
         theme(plot.title = element_text(hjust = 0.5))
plot3 

# Export the first scatterplot to project directory using ggsave.
ggsave("plot1.png",plot1)

```
 
In plot2 and plot3, the `color = ...` inside of  `aes()` are respectively numeric and factor variables, which correspond to gradient and discrete color scale, though in this case, the plot2 also shows only two colors.( Because only two value 0 or 1 can be taken).



